Model LF

### 2022-12-17 paper version 2.Rmd
Commit

@@

@@

@@

@@

### Compensation rates 
comp_r_fag= 0.55
comp_r_dp= 0.52
comp_r_sfc= 0.57

@@

#### Macro elasticity

@@

>>>>

## Baseline Scenario 4

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs4 <- list(

shock_wage_ds_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs4 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs4
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds

tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio

nl_g_bs4 = Shock_bs4$simulation$nl_g
unemp_bs4 = Shock_bs4$simulation$unemp
s_h_bs4 = Shock_bs4$simulation$s_h
inflation_bs4 = Shock_bs4$simulation$inflation

yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
prod_ds_bs4 = Shock_bs4$simulation$prod_ds
prod_ds_shock_bs4 = Shock_bs4$simulation$prod_ds_shock

ur_bs4 = Shock_bs4$simulation$ur
```

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList_4 <- list(
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

```{r}
# Simulate the model (following shock)
Shock_4 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_4
                    )
```

yk_ds_04 = Shock_4$simulation$yk_ds
emp_04 = Shock_4$simulation$emp
wage_ds_04 = Shock_4$simulation$wage_ds
ur_ds_04 = Shock_4$simulation$ur_ds
pc_ds_04 = Shock_4$simulation$pc_ds
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
pconk_ds_04 = Shock_4$simulation$pconk_ds
komp_r_04 = Shock_4$simulation$komp_r
max_dp_04 = Shock_4$simulation$max_dp
nben_h_04 = Shock_4$simulation$nben_h
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
ik_04 = Shock_4$simulation$ik
wage_ds_t_04 = Shock_4$simulation$wage_ds_t
nben_h_un_04 = Shock_4$simulation$nben_h_un
nl_g_04 = Shock_4$simulation$nl_g
nsben_h_04 = Shock_4$simulation$nsben_h
dp_person_04 = Shock_4$simulation$dp_person
part1_04 = Shock_4$simulation$part1
u_ds_04 = Shock_4$simulation$u_ds
kont_h_ratio_04 = Shock_4$simulation$kont_h_ratio
part_04 = Shock_4$simulation$part
unemp_04 = Shock_4$simulation$unemp
rw_ds_04 = Shock_4$simulation$rw_ds
kuld_04 = Shock_4$simulation$shock_kuld
inflation_04 = Shock_4$simulation$inflation
lf_04 = Shock_4$simulation$lf
prod_04 = Shock_4$simulation$prod
```

@@

### Section 4

@@

### Section 5

@@

### Compensation rates 
comp_r_fag= 0.55
comp_r_dp= 0.52
comp_r_sfc= 0.56

@@

#### elasticity of macro effects

@@

#### Full macro elasticity, using DØRS micro effects

e1_total= e2_micro + mean_e1_macro
e2_total= e2_micro + mean_e2_macro
e3_total= e2_micro + mean_e3_macro
